---
output:                                       html_document
editor_options:
  chunk_output_type: console
---

# POST ESTIMATION
## doing graphs of post-estimated choices over time using mean parameters of mixed models

```{r}
draws_rev_mix_fit_barre   <- read_csv("./results/draws__rev_mix__fit_gen_barre.csv")
draws_rev_mix_fit_chiffre <- read_csv("./results/draws__rev_mix__fit_gen_chiffre.csv")
draws_rev_mix_fit_exp2    <- read_csv("./results/draws__rev_mix__fit_gen_exp2.csv")

# here we run the code only for the graphical treatment of experiment 1 and the attraction effect

# experiment 1
  options <- read_csv("data/menus_cs_exp1.csv")
  options<-matrix(unlist(options), ncol=6,)
  J<-length(options[,1]) #(nr of menus)
  
  effect<-"attr"

    # graphical treatment
    treatment<-"exp1_barre"
    ndraws<-length(draws_rev_mix_fit_barre$alpha)
    N<-round(1000000/J,0) # number of draws to take up
    selected<-sample(ndraws, N, replace=TRUE)
    draws <- draws_rev_mix_fit_barre[selected,c(4:8,14,16)] 
  
    # numeric treatment
    # treatment<-"exp1_chiffre"
    # ndraws<-length(draws_rev_mix_fit_chiffre$alpha)
    # N<-round(1000000/J,0) # number of draws to take up
    # selected<-sample(ndraws, N, replace=TRUE)
    # draws <- draws_rev_mix_fit_chiffre[selected,c(4:8,14,16)]

# for experiment 2

  # treatment<-"exp2"
  # 
  # options <- read_csv("./data/menus_cs_exp2.csv")
  # options_a<-options[1:12,]
  # options_s<-options[13:24,]
  # options_c<-options[25:36,]
  # 
  # # then choose what effect to look at
  # effect<-"attr"
  # options<-options_a
  # # or
  # effect<-"sim"
  # options<-options_s
  # # or
  # effect<-"comp"
  # options<-options_c
  # 
  # #then
  # 
  # options<-matrix(unlist(options), ncol=6,)
  # J<-length(options[,1]) #(nr of menus)
  # 
  # # if keep all draws, too big matrix, so we select a sample of rows in draws
  # ndraws<-length(draws_rev_mix_fit_exp2$alpha)
  # N<-round(1000000/J,0) # number of draws to take up
  # selected<-sample(ndraws, N, replace=TRUE)
  # draws <- draws_rev_mix_fit_exp2[selected,c(4:8,14,16)] 

```


```{r}
# then generate rt post based on parameter estimates, given a choice above

# what parameters
k<-1
tau_sim<-0.1 # to introduce random choices at beginning


l<-1


rt_test<-matrix(data=NA,nrow=J*N,ncol=15)
for (j in (1:J)){
for (i in (1:N)){
  rt_test[((l-1)*N*J+(i+N*(j-1))),15]<-1;
  rt_test[((l-1)*N*J+(i+N*(j-1))),5:8]<-c(i,j,l,((l-1)*N*J+(i+N*(j-1))));
  rt_test[((l-1)*N*J+(i+N*(j-1))),9:14]<-options[j,];
  rt_test[((l-1)*N*J+(i+N*(j-1))),1:4]<-lba_rng(options[j,],k,draws$mu_I[i],draws$mu_m[i],draws$mu_lam[i],draws$mu_gamma[i],draws$mu_beta[i],draws$mu_stay[i],tau_sim,draws$alpha[i])
  }
}

# save rttest depending on situation chosen above
write.csv(rt_test,file=paste("./results/post_estimates_",treatment,"_",effect,".csv",sep=""), row.names = FALSE)
```


## graphing post_estimates

```{r}

# we run this only for the attraction effect in experiment 1, graphical treatment, for illustration

effect<-"attr"
#effect<-"sim"
#effect<-"comp"

# and

treatment<-"exp1_barre"
#treatment<-"exp1_chiffre"
#treatment<-"exp2"

rt_test<-read.csv(paste("./results/post_estimates_",treatment,"_",effect,".csv",sep=""))

#then

# consider when no choices is made in the imparted time
length(rt_test[rt_test[,1]<1,])
length(rt_test)
#rt_test<-rt_test[rt_test[,1]<1,]
1-length(rt_test[rt_test[,1]<1,])/length(rt_test)

# we compute how many switch in choices there are by looking at how many t2=1 there are, in proportions (those are no switch)
1-length(rt_test[rt_test[,3]==1,1])/length(rt_test[,1]) 


# checking the shares


# first choices
table_ex_xtabs1 <- xtabs(~V2, data=rt_test)
table_ex_xtabs1/(J*N)

# second choices, by menu
table_ex_xtabs2 <- xtabs(~V4, data=rt_test)
table_ex_xtabs2/(J*N)

# choice shares over time
# do graphs using # share choice function in "model and simulation"
share_graph(rt_test,paste(treatment,"_",effect,sep=""))


```

## ALTERNATIVE TO CHECK THERE IS NO DIFFERENCE WHETHER WE USE MEAN INDIVIDUAL ESTIMATES OR A DRAW OF INDIVIDUAL ESTIMATES
## doing graphs of post-estimated choices over time using individual parameters of mixed models

```{r}

draws_rev_mix_fit_barre   <- read_csv("./results/draws__rev_mix__fit_gen_barre.csv")
draws_rev_mix_fit_chiffre <- read_csv("./results/draws__rev_mix__fit_gen_chiffre.csv")
draws_rev_mix_fit_exp2    <- read_csv("./results/draws__rev_mix__fit_gen_exp2.csv")

# we run this only for menus in experiment 1, graphical treatment, for illustration

options <- read_csv("./data/menus_cs_exp1.csv")
options<-matrix(unlist(options), ncol=6,)
J<-length(options[,1]) #(nr of menus)
effect<-"attraction"

# for graphical treatment

treatment<-"exp1_barre"
indiv<-63
draws<-draws_rev_mix_fit_barre[,c(4:8,14,16)]
ndraws<-length(draws_rev_mix_fit_barre$alpha)
N<-round(1000000/indiv/J,0) # number of draws to take up
selected<-sample(ndraws, N)
draws_id <- draws_rev_mix_fit_barre[selected,c(16:(6*indiv+16))] 

# for numeric treatment

# treatment<-"exp1_chiffre"
# indiv<-48
# draws<-draws_rev_mix_fit_chiffre[,c(4:8,14,16)]
# ndraws<-length(draws_rev_mix_fit_chiffre$alpha)
# N<-round(1000000/indiv/J,0) # number of draws to take up
# selected<-sample(ndraws, N)
# draws_id <- draws_rev_mix_fit_chiffre[selected,c(16:(6*indiv+16))]

# for experiment 2

# treatment<-"exp2"
# 
# options <- read_csv("./data/menus_cs_exp2.csv")
# options_a<-options[1:12,]
# options_s<-options[13:24,]
# options_c<-options[25:36,]
# 
# # then either
# effect<-"attraction"
# options<-options_a
# # or
# effect<-"similarity"
# options<-options_s
# # or
# effect<-"compromise"
# options<-options_c
# 
# 
# options<-matrix(unlist(options), ncol=6,)
# J<-length(options[,1]) #(nr of menus)
# 
# indiv<-198
# draws<-draws_rev_mix_fit_exp2[,c(4:8,14,16)]
# ndraws<-length(draws_rev_mix_fit_exp2$alpha)
# N<-round(1000000/indiv/J,0) # number of draws to take up
# selected<-sample(ndraws, N)
# draws_id <- draws_rev_mix_fit_exp2[selected,c(16:(6*indiv+16))] 



# then extract parameters

draws_id_alpha <- as.matrix(draws_id[,1])
draws_id_I <- as.matrix(draws_id[,c((2):(1+indiv))])
draws_id_m <- as.matrix(draws_id[,c((2+indiv):(1+2*indiv))])
draws_id_lam <- as.matrix(draws_id[,c((2+2*indiv):(1+3*indiv))])
draws_id_gamma <- as.matrix(draws_id[,c((2+3*indiv):(1+4*indiv))])
draws_id_beta <- as.matrix(draws_id[,c((2+4*indiv):(1+5*indiv))])
draws_id_stay <- as.matrix(draws_id[,c((2+5*indiv):(1+6*indiv))])


# what parameters
k<-1
tau_sim<-0.01 # to introduce random choices at beginning
# if keep all draws, too big matrix


rt_test<-matrix(data=NA,nrow=J*N*indiv,ncol=15)
for(l in (1:indiv)){
for (j in (1:J)){
for (i in (1:N)){
  rt_test[((l-1)*N*J+(i+N*(j-1))),15]<-1;
  rt_test[((l-1)*N*J+(i+N*(j-1))),5:8]<-c(i,j,l,((l-1)*N*J+(i+N*(j-1))));
  rt_test[((l-1)*N*J+(i+N*(j-1))),9:14]<-options[j,];
  rt_test[((l-1)*N*J+(i+N*(j-1))),1:4]<-lba_rng(options[j,],k,draws_id_I[i,l],draws_id_m[i,l],draws_id_lam[i,l],draws_id_gamma[i,l],draws_id_beta[i,l],draws_id_stay[i,l],tau_sim,draws_id_alpha[i])
  }
}
}


# save rttest depending on situation as
rt_test_exp1_barre_attr<-rt_test
#rt_test_exp1_chiffre_attr<-rt_test
#rt_test_exp2_attr<-rt_test
#rt_test_exp2_sim<-rt_test
#rt_test_exp2_comp<-rt_test

#summary(rt_test)
#View(rt_test)
#hist(rt_test[,1],probability=T)

# get rid of no choices
length(rt_test[rt_test[,1]<1,])
length(rt_test)
#rt_test<-rt_test[rt_test[,1]<1,]
1-length(rt_test[rt_test[,1]<1,])/length(rt_test)

# we compute how many switch in choices there are by looking at how many t2=1 there are, in proportions (those are no switch)
1-length(rt_test[rt_test[,3]==1,1])/length(rt_test[,1]) 


# checking the shares


# first choices
table_ex_xtabs1 <- xtabs(~V2, data=rt_test)
table_ex_xtabs1/(J*N*indiv)

# second choices, by menu
table_ex_xtabs2 <- xtabs(~V4, data=rt_test)
table_ex_xtabs2/(J*N*indiv)

# choice shares over time
# do graphs using # share choice function in "data and regression"
share_graph(rt_test,paste(treatment,"_",effect,sep=""))

# still need to do transition tables
# for this go to step 1 and choose to save tables in Postestimated_graphs

```

## alternative way to compute speed, precision and bias using draws of individual parameters of mixed models and with example options

```{r}

draws_rev_mix_fit_barre   <- read_csv("./results/draws__rev_mix__fit_gen_barre.csv")
draws_rev_mix_fit_chiffre <- read_csv("./results/draws__rev_mix__fit_gen_chiffre.csv")
draws_rev_mix_fit_exp2    <- read_csv("./results/draws__rev_mix__fit_gen_exp2.csv")

# choose what options to do among the three, here we will do only attraction for illustration purposes

effect<-"attraction"
options<-options_a

# alternatively

#effect<-"similarity"
#options<-options_s

#or

#effect<-"compromise"
#options<-options_c


#then

options<-matrix(unlist(options), ncol=6,)
J<-length(options[,1]) #(nr of menus)


# choose what experiment we look at, here we do only the graphical treatment in experiment 1
# if barre
treatment<-"exp1_barre"
indiv<-63
ndraws<-length(draws_rev_mix_fit_barre$alpha)
N<-round(1000000/indiv/J,0) # number of draws to take up
selected<-sample(ndraws, N)
draws_id <- draws_rev_mix_fit_barre[selected,c(16:(6*indiv+16))] 

# if chiffre
# treatment<-"exp1_chiffre"
# indiv<-48
# ndraws<-length(draws_rev_mix_fit_chiffre$alpha)
# N<-round(1000000/indiv/J,0) # number of draws to take up
# selected<-sample(ndraws, N)
# draws_id <- draws_rev_mix_fit_chiffre[selected,c(16:(6*indiv+16))]

# for experiment 2

# treatment<-"exp2"
# indiv<-198
# ndraws<-length(draws_rev_mix_fit_exp2$alpha)
# N<-round(1000000/indiv/J,0) # number of draws to take up
# selected<-sample(ndraws, N)
# draws_id <- draws_rev_mix_fit_exp2[selected,c(16:(6*indiv+16))] 

# then extract parameters

draws_id_alpha <- as.matrix(draws_id[,1])
draws_id_I <- as.matrix(draws_id[,c((2):(1+indiv))])
draws_id_m <- as.matrix(draws_id[,c((2+indiv):(1+2*indiv))])
draws_id_lam <- as.matrix(draws_id[,c((2+2*indiv):(1+3*indiv))])
draws_id_gamma <- as.matrix(draws_id[,c((2+3*indiv):(1+4*indiv))])
draws_id_beta <- as.matrix(draws_id[,c((2+4*indiv):(1+5*indiv))])
draws_id_stay <- as.matrix(draws_id[,c((2+5*indiv):(1+6*indiv))])

#View(draws_id_I)


# what parameters
k<-1
tau_sim<-0.01 # to introduce random choices at beginning
# if keep all draws, too big matrix

i<-j<-l<-1
draws_id_m[i,l]

c(options[j,],k,draws_id_I[i,l],draws_id_m[i,l],draws_id_lam[i,l],draws_id_gamma[i,l],draws_id_beta[i,l])

getDrifts(options[j,],draws_id_I[i,l],draws_id_m[i,l],draws_id_lam[i,l],draws_id_gamma[i,l],draws_id_beta[i,l])


rt_test<-matrix(data=NA,nrow=J*N*indiv,ncol=21)
for(l in (1:indiv)){
for (j in (1:J)){
for (i in (1:N)){
  rt_test[((l-1)*N*J+(i+N*(j-1))),1:4]<-c(i,j,l,((l-1)*N*J+(i+N*(j-1))));
  rt_test[((l-1)*N*J+(i+N*(j-1))),5:10]<-options[j,];
  rt_test[((l-1)*N*J+(i+N*(j-1))),11:13]<-getDrifts(options[j,],draws_id_I[i,l],draws_id_m[i,l],draws_id_lam[i,l],draws_id_gamma[i,l],draws_id_beta[i,l]); #drifts first choice  
  rt_test[((l-1)*N*J+(i+N*(j-1))),14]<-(draws_id_I[i,l]+0.15*draws_id_gamma[i,l])/gamma(1+1/draws_id_alpha[i]); #this is speed if there was a value difference of 0.6/4 between options, as between T and D
  rt_test[((l-1)*N*J+(i+N*(j-1))),15]<-((draws_id_I[i,l]+0.15*draws_id_gamma[i,l])/max(draws_id_I[i,l]-0.15*draws_id_gamma[i,l],0.00000000001))^draws_id_alpha[i]/(1+((draws_id_I[i,l]+0.15*draws_id_gamma[i,l])/max(draws_id_I[i,l]-0.15*draws_id_gamma[i,l],0.00000000001))^draws_id_alpha[i]); #this is precision if there was a value difference of 0.6/4. Note need to set =1 if second is negative
  rt_test[((l-1)*N*J+(i+N*(j-1))),16:18]<-(getDrifts(options[j,],draws_id_I[i,l],draws_id_m[i,l],draws_id_lam[i,l],draws_id_gamma[i,l],draws_id_beta[i,l])-draws_id_I[i,l])/draws_id_gamma[i,l]; # this is the value differences   
  rt_test[((l-1)*N*J+(i+N*(j-1))),19]<-sd(rt_test[((l-1)*N*J+(i+N*(j-1))),18:20]); # this is bias
  rt_test[((l-1)*N*J+(i+N*(j-1))),20]<-draws_id_stay[i,l]; # this is the stay parameter
  rt_test[((l-1)*N*J+(i+N*(j-1))),21]<-draws_id_alpha[i]; # this is the alpha parameter
}
}
}

rt_test[,19]<-rowSds(as.matrix(rt_test[,16:18]))

# then take averages for each individual, stored in column 3
rt_test<-as.tibble(rt_test)

rt_test_means <- rt_test %>%
  group_by(V3) %>%
  summarise_all(mean)  

data<-cbind(rt_test_mean[rt_test_mean$treatment==1,c("speed","precision","bias_a","stay")],rt_test_means[,c(14,15,19,20)])

plot(data$bias, data$V19, pch = 19, col = "lightblue")
plot(data$speed, data$V14, pch = 19, col = "lightblue")
plot(data$precision, data$V15, pch = 19, col = "lightblue")
plot(data$stay, data$V20, pch = 19, col = "lightblue")




```
