---
output:                                       html_document
editor_options:
  chunk_output_type: console
---

# ESTIMATION

## loading and storing data from experiment 1

```{r}

First_two_choices <- read.csv2("./data/First_five_choices_exp1.csv", sep=",")


treatment<-car::recode(First_two_choices$treatment, "'barres'= 0 ; 'chiffres'= 1")
type<-car::recode(First_two_choices$screentype, "'3 options CS'= 1 ; '3 options noCS'= 0; '2 options'= 2")
choice1<-car::recode(First_two_choices$choice_1, "'target'= 1 ; 'competitor'= 2; 'decoy'= 3")
choice2<-car::recode(First_two_choices$choice_2, "'target'= 1 ; 'competitor'= 2; 'decoy'= 3")
choice2[is.na(choice2)] <- choice1[is.na(choice2)]
time1<-First_two_choices$time_1/20000
time2<-First_two_choices$time_2/20000
time2[is.na(time2)] <- 1
t2<-(time2-time1)*(time2<1)

up<-cbind(as.numeric(First_two_choices$up_target),as.numeric(First_two_choices$up_competitor),as.numeric(First_two_choices$up_decoy))
p<-cbind(as.numeric(First_two_choices$price_target),as.numeric(First_two_choices$price_competitor),as.numeric(First_two_choices$price_decoy))
q<-cbind(as.numeric(First_two_choices$size_target),as.numeric(First_two_choices$size_competitor),as.numeric(First_two_choices$size_decoy))
id<-First_two_choices$id

summary(p)
# p goes from 60 to 405 (in practice) and 0 to 500 (in theory)
# we set pmax to 500
# then pmin is 60/500 of pmax
pmin<-60
pmax<-500

lp<-log(1/p)-log(1/pmax)


summary(q)
# q goes from 90 to 250 (in practice) and 0 to 300 (in theory)
# we set qmin/qmax to correspond in proportion to pmin/pmax
qmax<-300
qmin<-qmax/pmax*pmin
# we obtain qmin=36


lq<-log(q)-log(qmin)


# putting into form as rt

#cbind(time1,time2)
rt = cbind(time1,choice1,time2,choice2,type,up,lp[,1],lq[,1],lp[,2],lq[,2],lp[,3],lq[,3],id,t2,treatment)
rt<-as.data.frame(rt)

rt<-na.omit(rt) #this gets rid of all 2 menus and of all try out menus and menus with no choice made

write.csv(rt,file="./data/rt_exp_1.csv", row.names = FALSE)

# saving menus with a CS and three options

menus_cs_exp1<-rt[rt$type==1&rt$id==626312,][,9:14]
write.csv(menus_cs_exp1,file="./data/menus_cs_exp1.csv", row.names = FALSE)



# load data locally for estimation
rt<-read.csv("./data/rt_exp_1.csv")


# selecting menus with a CS and three options

rts_exp1<-rt[rt$type==1,1:17]

# separating graphical (bar) and numeric (chifr) treatment in experiment 1

rts_bar<-rts_exp1[rts_exp1$treatment==0,1:15]

rts_chifr<-rts_exp1[rts_exp1$treatment==1,1:15]


```

## loading and storing data from experiment 2

```{r}
# experiment 2

First_two_choices <- read.csv2("./data/First_two_choices_exp2.csv", sep=",")
describe(First_two_choices)


type<-car::recode(First_two_choices$type, "'decoy'= 1 ; 'similarity'= 2; 'compromise'= 3")
# 1 is attraction effect, 2 is similarity, 3 is compromise --> asc
choice1<-car::recode(First_two_choices$choice_1, "'target'= 1 ; 'competitor'= 2; 'decoy'= 3")
# 1 2 3 are t, c, d
choice2<-car::recode(First_two_choices$choice_2, "'target'= 1 ; 'competitor'= 2; 'decoy'= 3")
choice2[is.na(choice2)] <- choice1[is.na(choice2)]
time1<-First_two_choices$time_1/20000
time2<-First_two_choices$time_2/20000
time2[is.na(time2)] <- 1
t2<-(time2-time1)*(time2<1)

p<-cbind(as.numeric(First_two_choices$p1),as.numeric(First_two_choices$p2),as.numeric(First_two_choices$p3))
q<-cbind(as.numeric(First_two_choices$q1),as.numeric(First_two_choices$q2),as.numeric(First_two_choices$q3))
up<-p/q
summary(up)

id<-as.numeric(factor(First_two_choices$subject))

summary(p)
# p goes from 80 to 300 (in practice) and 0 to 500 (in theory)
# we set pmax to 500
# then pmin is 60/500 of pmax
pmin<-60
pmax<-500

lp<-log(1/p)-log(1/pmax)
summary(lp)


summary(q)
# q goes from 80 to 311 (in practice) and 0 to 500 (in theory)
# we set qmin/qmax to correspond in proportion to pmin/pmax
qmax<-500
qmin<-qmax/pmax*pmin


lq<-log(q)-log(qmin)

summary(lq)

plot(lp,lq)

# putting into form as rt

#cbind(time1,time2)
rt = cbind(time1,choice1,time2,choice2,type,up,lp[,1],lq[,1],lp[,2],lq[,2],lp[,3],lq[,3],id,t2)

rt<-as.data.frame(rt)

# save menus

menus_cs_exp2<-rt[rt$type!="2menu"&rt$id==1,][,9:14]
write.csv(menus_cs_exp2,file="./data/menus_cs_exp2.csv", row.names = FALSE)


rt<-na.omit(rt) #this gets rid of all 2 menus and of all try out menus and cases where no choice made
len = length(rt[,1])
describe(rt)

write.csv(rt,file="./data/rt_exp_2.csv", row.names = FALSE)


# load data locally for estimation
rt<-read.csv("./data/rt_exp_2.csv")


rts_exp2<-rt



```

# Evaluation with variational method

```{r}
## warning: you need to run many chains and check convergence systematically
## in the following we run only one chain for illustration purpose, but the paper is based on running 16 chains for each regressions, and checking convergence chain by chain


# loading models

# model for first choices

mod <- cmdstan_model('mlba_single_v8_Frechet_generalized.stan')

# model for revised choices

mod_rev2 <- cmdstan_model('mlba_revision_v9_Frechet_generalized.stan')

# model with fixed effects

mod_rev_mix2 <- cmdstan_model('mlba_revision_v9_Frechet_generalized_mixed.stan')
```

## choosing what dataset to run the model on

```{r}
# choose what dataset to run the model on
# here, we run the code for 
# experiment 1, graphical treatment
# the code for other sub-experiments is commented out

treatment<-"barre"; rts<-rts_bar;
N_bar=max(as.integer((factor(rts[,15], levels=unique(rts[,15])))))


# experiment 1, numeric treatment
treatment<-"chiffre"; rts<-rts_chifr;
N_chiffre=max(as.integer((factor(rts[,15], levels=unique(rts[,15])))))

# experiment 2
treatment<-"exp2"; rts<-rts_exp2;
N_exp2=max(as.integer((factor(rts[,15], levels=unique(rts[,15])))))
```

## setting parameters for estimates including starting values

```{r}

working_dir<-"./"

ndraws<-2000 # we draw 2000 samples post estimation
nchains<-1 # we do 16 chains for full estimations, we set nchains=1 here for demonstration purpose

# starting parameters are chosen to be relatively neutral and consistent with past estimations.

I<-1; m<-1; lam<-0.5; gamma<-3; beta<-1; k<-1; alpha<-1; stay<-1; tau<-0.0; 

# labeling and computing the number of individuals in the dataset, for mixed estimations 
rts[,15]<-as.integer((factor(rts[,15], levels=unique(rts[,15]))))
NUM_INDIV=max(as.integer((factor(rts[,15], levels=unique(rts[,15])))))

# setting starting values for mixed estimation

k2<-rep(k,NUM_INDIV)
tau2<-rep(tau,NUM_INDIV)
I2<-rep(I,NUM_INDIV)
m2<-rep(m,NUM_INDIV)
lam2<-rep(lam,NUM_INDIV)
gamma2<-rep(gamma,NUM_INDIV)
beta2<-rep(beta,NUM_INDIV)
stay2<-rep(stay,NUM_INDIV)
```

## regressions for first choices only (this can take quite a while, so not run as a default!)

```{r eval=FALSE, include=FALSE}
for (i in (1:nchains)){

fit <- mod$variational(
  data = list(RT=rts[,1:14], LENGTH=length(rts[,1]), NUM_CHOICES=3),
  iter = 10000,
  output_samples = ndraws,
  init=function () list(k=k,tau=tau,I=I,m=m,lam=lam,gamma=gamma,beta=beta,alpha=alpha),
  output_dir = working_dir,
  output_basename = paste("./results/fit_gen_",treatment,"_",i,sep = ""),
  save_latent_dynamics=TRUE,
  algorithm="meanfield",
  tol_rel_obj=0.001,
  grad_samples = 1,
  elbo_samples = 100)

fit$summary()
write.csv(fit$draws(format = "df"),file=paste("./results/post_fit_draws_gen_",treatment,"_",i,".csv",sep=""))
fit$save_latent_dynamics_files(dir = , basename = paste("./results/post_fit_latent_gen_","_",i,treatment,sep=""), timestamp = FALSE, random = FALSE)
}
```

## regressions including revisions in choices (this can take quite a while so not run as a default!)

```{r eval=FALSE, include=FALSE}
for (i in (1:nchains)){

fit <- mod_rev2$variational(
  data = list(RT=rts[,1:14], LENGTH=length(rts[,1]), NUM_CHOICES=3),
  iter = 10000,
  output_samples = ndraws,
  init=function () list(I=I,m=m,lam=lam,gamma=gamma,beta=beta,stay=stay,alpha=alpha),
  output_dir = working_dir,
  output_basename = paste("./results/rev_fit_gen_",treatment,"_",i,sep = ""),
  save_latent_dynamics=TRUE,
  algorithm="meanfield",
  tol_rel_obj=0.001,
  elbo_samples = 100)
fit$summary()

write.csv(fit$draws(format = "df"),file=paste("./results/post_rev_fit_draws_gen_",treatment,"_",i,".csv",sep=""))
fit$save_latent_dynamics_files(dir = , basename = paste("./results/post_rev_fit_latent_gen_","_",i,treatment,sep=""), timestamp = FALSE, random = FALSE)
}
```

## Regressions with revisions in choice and mixed effects (this can take quite a while so not run as a default!)

```{r eval=FALSE, include=FALSE}

for (i in (1:nchains)){
fit <- mod_rev_mix2$variational(
  data = list(
    RT=rts[,1:15],
    LENGTH=length(rts[,1]),
    NUM_CHOICES=3,
    NUM_INDIV=NUM_INDIV
    ),
  init=function () list(I=I2,m=m2,lam=lam2,gamma=gamma2,beta=beta2,stay=stay2,alpha=alpha,mu_I=I,mu_m=m,mu_lam=lam,mu_gamma=gamma,mu_beta=beta,mu_stay=stay,tau_I=I,tau_m=m,tau_lam=lam,tau_gamma=gamma,tau_beta=beta,tau_stay=stay),
  iter = 10000,
  output_samples = ndraws,
  output_dir = working_dir,
  output_basename = paste("./results/rev_mix_fit_gen_",treatment,"_",i,sep = ""),
  save_latent_dynamics=TRUE,
  algorithm="meanfield",
  tol_rel_obj=0.005,
  grad_samples = 1,
  elbo_samples = 100)

fit$summary()
write.csv(fit$draws(format = "df"),file=paste("./results/post_rev_mix_fit_draws_gen_",treatment,"_",i,".csv",sep=""))
fit$save_latent_dynamics_files(dir = , basename = paste("./results/post_rev_mix_fit_latent_gen_","_",i,treatment,sep=""), timestamp = FALSE, random = FALSE)
}


```

## checking convergence chain by chain, then storing draws and summary tables of estimates

```{r}

nchains<-1 # full results rely on 16 chains
ndraws<-2000

# choose what treatment to look at, here we limit ourselves to experiment 1, graphical treatment for demonstration purpose

treatment<-"barre";

# experiment 1, numeric treatment

#treatment<-"chiffre";

# experiment 2

#treatment<-"exp2";


# then look at type of estimate, here we limit ourselves to single estimates for demonstration purpose

# single estimates

type<-"_"


# for rev estimates

#type<-"_rev_"


# for mixed estimates

#type<-"_rev_mix_"




# vector to store chains
{
draws<-vector("list",nchains)

# put all draws from all chains together for the treatment and model chosen

for(i in 1:nchains){
draws[[i]]<-read_csv(paste("./results/post",type,"fit_draws_gen_",treatment,"_",i,".csv", sep=""))
}

# concatenate all draws on all chains, for demonstration purpose only one

fit<-rbind(draws[[1]])


#fit<-rbind(draws[[1]],draws[[2]],draws[[3]],draws[[4]],draws[[5]],draws[[6]],draws[[7]],draws[[8]],draws[[9]],draws[[10]],draws[[11]],draws[[12]],draws[[13]],draws[[14]],draws[[15]],draws[[16]],draws[[17]],draws[[18]],draws[[19]],draws[[20]])

# process and add column with draw number

fit<-fit[,-1]
fit<-as.data.frame(fit)
a<-c(t(matrix(t(rep(1:nchains,ndraws)),nrow=nchains,ncol=ndraws)))
#a<-c(t(matrix(t(rep(1:18,ndraws)),nrow=18,ncol=ndraws)))

fit$.draw<-a
fit$Chain<-a


write.csv(fit,file=paste("./results/draws_",type,"_fit_gen_",treatment,".csv",sep=""))
write.csv(summarise_draws(fit),file=paste("./results/summary_",type,"_fit_gen_",treatment,".csv",sep=""))
}

summarise_draws(fit)
# checking the draws chain by chain, and identifying if some are different from others
# note, for this we need several chains, so we do not run mcmc_violin it in this file which is for demonstration purposes

mcmc_trace(fit,pars=c("lp__"))
#mcmc_violin(fit,pars=c("lp__"))

# for single estimates

mcmc_hist(fit,pars=c("I","gamma","m","lam","beta","alpha"))
mcmc_trace(fit[,],pars=c("I","gamma","m","lam","beta","alpha"))
#mcmc_violin(fit,pars=c("I","gamma","m","lam","beta","alpha"))


# for rev estimates

#mcmc_hist(fit,pars=c("I","gamma","m","lam","beta","alpha","stay"))
#mcmc_trace(fit[,],pars=c("I","gamma","m","lam","beta","alpha","stay"))
#mcmc_violin(fit,pars=c("I","gamma","m","lam","beta","alpha","stay"))

# for mixed estimates

#mcmc_hist(fit,pars=c("mu_I","mu_gamma","mu_m","mu_lam","mu_beta","alpha","mu_stay"))
#mcmc_trace(fit[,],pars=c("mu_I","mu_gamma","mu_m","mu_lam","mu_beta","alpha","mu_stay"))
#mcmc_violin(fit,pars=c("mu_I","mu_gamma","mu_m","mu_lam"))
#mcmc_violin(fit,pars=c("mu_beta","alpha","mu_stay"))


# saving post estimates and summary table of estimates



```

# formatting and presenting results of estimation

## summary table of model estimation results

```{r}

# this part uses stored estimates from the estimate files

summary_single_fit_barre   <- read_csv("./results/summary___fit_gen_barre.csv")
summary_single_fit_chiffre <- read_csv("./results/summary___fit_gen_chiffre.csv")
summary_single_fit_exp2    <- read_csv("./results/summary___fit_gen_exp2.csv")
summary_rev_fit_barre   <- read_csv("./results/summary__rev__fit_gen_barre.csv")
summary_rev_fit_chiffre <- read_csv("./results/summary__rev__fit_gen_chiffre.csv")
summary_rev_fit_exp2    <- read_csv("./results/summary__rev__fit_gen_exp2.csv")
summary_rev_mix_fit_barre   <- read_csv("./results/summary__rev_mix__fit_gen_barre.csv")
summary_rev_mix_fit_chiffre <- read_csv("./results/summary__rev_mix__fit_gen_chiffre.csv")
summary_rev_mix_fit_exp2    <- read_csv("./results/summary__rev_mix__fit_gen_exp2.csv")


formatted_single_fit_barre <- summary_single_fit_barre %>%
  mutate_if(is.numeric, round, 2) %>%
  slice(c(c(1:8))) %>%
  select(variable, mean = mean, low = q5, hi = q95, eff = ess_bulk) %>%
  mutate(confint = paste0("[", low ,";",hi,"]")) %>%
  select(variable,mean,confint,eff)

formatted_single_fit_chiffre <- summary_single_fit_chiffre %>%
  mutate_if(is.numeric, round, 2) %>%
  slice(c(c(1:8))) %>%
  select(variable, mean = mean, low = q5, hi = q95, eff = ess_bulk) %>%
  mutate(confint = paste0("[", low ,";",hi,"]")) %>%
  select(mean,confint,eff)

formatted_single_fit_exp2 <- summary_single_fit_exp2 %>%
  mutate_if(is.numeric, round, 2) %>%
  slice(c(c(1:8))) %>%
  select(variable, mean = mean, low = q5, hi = q95, eff = ess_bulk) %>%
  mutate(confint = paste0("[", low ,";",hi,"]")) %>%
  select(mean,confint,eff)


formatted_rev_fit_barre <- summary_rev_fit_barre %>%
  mutate_if(is.numeric, round, 2) %>%
  slice(c(c(1:9))) %>%
  select(variable, mean = mean, low = q5, hi = q95, eff = ess_bulk) %>%
  mutate(confint = paste0("[", low ,";",hi,"]")) %>%
  select(variable,mean,confint,eff)

formatted_rev_fit_chiffre <- summary_rev_fit_chiffre %>%
  mutate_if(is.numeric, round, 2) %>%
  slice(c(c(1:9))) %>%
  select(variable, mean = mean, low = q5, hi = q95, eff = ess_bulk) %>%
  mutate(confint = paste0("[", low ,";",hi,"]")) %>%
  select(mean,confint,eff)

formatted_rev_fit_exp2 <- summary_rev_fit_exp2 %>%
  mutate_if(is.numeric, round, 2) %>%
  slice(c(c(1:9))) %>%
  select(variable, mean = mean, low = q5, hi = q95, eff = ess_bulk) %>%
  mutate(confint = paste0("[", low ,";",hi,"]")) %>%
  select(mean,confint,eff)


formatted_rev_mix_fit_barre <- summary_rev_mix_fit_barre  %>%
  mutate_if(is.numeric, round, 2) %>%
  slice(c(c(1:15))) %>%
  select(variable, mean = mean, low = q5, hi = q95, eff = ess_bulk) %>%
  mutate(confint = paste0("[", low ,";",hi,"]")) %>%
  select(variable,mean,confint,eff)

formatted_rev_mix_fit_chiffre <- summary_rev_mix_fit_chiffre  %>%
  mutate_if(is.numeric, round, 2) %>%
  slice(c(c(1:15))) %>%
  select(variable, mean = mean, low = q5, hi = q95, eff = ess_bulk) %>%
  mutate(confint = paste0("[", low ,";",hi,"]")) %>%
  select(mean,confint,eff)

formatted_rev_mix_fit_exp2 <- summary_rev_mix_fit_exp2  %>%
  mutate_if(is.numeric, round, 2) %>%
  slice(c(c(1:15))) %>%
  select(variable, mean = mean, low = q5, hi = q95, eff = ess_bulk) %>%
  mutate(confint = paste0("[", low ,";",hi,"]")) %>%
  select(mean,confint,eff)


tab <- bind_cols(formatted_single_fit_barre, formatted_single_fit_chiffre,formatted_single_fit_exp2)

colnames(tab) <- c("Parameters","Mean","$90\\%$ CI","$N_{eff}$","Mean","$90\\%$ CI","$N_{eff}$","Mean","$90\\%$ CI","$N_{eff}$")

tab$Parameters<-c("$LL$","$LL_a$","$I$","$m$","$\\lambda$","$\\gamma$","$\\beta$","$\\alpha$")


x=kable(tab, format = "latex", caption = "Parameter estimates, model with only first choices", booktabs = TRUE, digits=2, escape=F) %>% save_kable(".\\tables\\tab_single.tex")


as.pdf(tab, stem="tab_single")
file.rename(from="tab_single.pdf",to="./tables/tab_single.pdf")


tab <- bind_cols(formatted_rev_fit_barre, formatted_rev_fit_chiffre,formatted_rev_fit_exp2)

colnames(tab) <- c("Parameters","Mean","$90\\%$ CI","$N_{eff}$","Mean","$90\\%$ CI","$N_{eff}$","Mean","$90\\%$ CI","$N_{eff}$")

tab$Parameters<-c("$LL$","$LL_a$","$I$","$m$","$\\lambda$","$\\gamma$","$\\beta$","$\\stay$","$\\alpha$")


x=kable(tab, format = "latex", caption = "Parameter estimates, model with revisions", booktabs = TRUE, digits=2, escape=F) %>% save_kable(".\\tables\\tab_rev.tex")

as.pdf(tab, stem="tab_rev")
file.rename(from="tab_rev.pdf",to="./tables/tab_rev.pdf")


tab <- bind_cols(formatted_rev_mix_fit_barre, formatted_rev_mix_fit_chiffre,formatted_rev_mix_fit_exp2)

colnames(tab) <- c("Parameters","Mean","$90\\%$ CI","$N_{eff}$","Mean","$90\\%$ CI","$N_{eff}$","Mean","$90\\%$ CI","$N_{eff}$")

tab$Parameters<-c("$LL$","$LL_a$","$\\mu_I$","$\\mu_m$","$\\mu_\\lambda$","$\\mu_{\\gamma}$","$\\mu_{\\beta}$","$\\tau_I$","$\\tau_m$","$\\tau_{\\lambda}$","$\\tau_{\\gamma}$","$\\tau_{\\beta}$","$\\mu_{\\stay}$","$\\tau_{\\stay}$","$\\alpha$")


x=kable(tab, format = "latex", caption = "Parameter estimates, mixed model with revisions", booktabs = TRUE, digits=2, escape=F) %>% save_kable(".\\tables\\tab_mixed.tex")

as.pdf(tab, stem="tab_mix_rev")
file.rename(from="tab_mix_rev.pdf",to="./tables/tab_mix_rev.pdf")
```

## extracting individual parameter estimates from mixed estimations and doing summary tables of individual estimates


```{r}

# this uses extracted summary estimates above

######################
#Barre
#######################

formatted_rev_mix_fit_barre_id <- summary_rev_mix_fit_barre %>% 
  slice(c(15:393))%>%                                #selecting the right rows
  separate("variable", c("param", "id")) %>%    # splitting parameter and id
  mutate(id = as.numeric(id)) %>%                  # ID was a character, fixing (not so important but hey)
  select(id, param, mean) %>%                      # selecting only the needed variables
  pivot_wider(names_from = param, values_from = mean)

formatted_rev_mix_fit_barre_id$alpha<-rep(formatted_rev_mix_fit_barre_id$alpha[1],64)
formatted_rev_mix_fit_barre_id<-formatted_rev_mix_fit_barre_id[-1,]
#formatted_rev_mix_fit_barre_id<-formatted_rev_mix_fit_barre_id[,-c(2:3)]

# chiffre
#########################

formatted_rev_mix_fit_chiffre_id <- summary_rev_mix_fit_chiffre %>% 
  slice(c(15:303)) %>%                                #selecting the right rows
  separate("variable", into = c("param", "id")) %>%    # splitting parameter and id
  mutate(id = as.numeric(id)) %>%                  # ID was a character, fixing (not so 
  select(id, param, mean) %>%                      # selecting only the needed variables
  pivot_wider(names_from = param, values_from = mean)

formatted_rev_mix_fit_chiffre_id$alpha<-rep(formatted_rev_mix_fit_chiffre_id$alpha[1],49)
formatted_rev_mix_fit_chiffre_id<-formatted_rev_mix_fit_chiffre_id[-1,]



##########################
# experiment 2
#########################

formatted_rev_mix_fit_exp2_id <- summary_rev_mix_fit_exp2 %>% 
  slice(c(15:1203)) %>%                                #selecting the right rows
  separate("variable", into = c("param", "id")) %>%    # splitting parameter and id
  mutate(id = as.numeric(id)) %>%                  # ID was a character, fixing (not so important but hey)
  select(id, param, mean) %>%                      # selecting only the needed variables
  pivot_wider(names_from = param, values_from = mean)

formatted_rev_mix_fit_exp2_id$alpha<-rep(formatted_rev_mix_fit_exp2_id$alpha[1],199)
formatted_rev_mix_fit_exp2_id<-formatted_rev_mix_fit_exp2_id[-1,]


# doing tables of average individual estimates


quant <- function(x, prob, ...) quantile(x, prob=c(.05, .95),na.rm=TRUE)

barre_mix<-as.tibble(cbind(colMeans(formatted_rev_mix_fit_barre_id),t(apply(formatted_rev_mix_fit_barre_id, 2, FUN = quant))))

chiffre_mix<-as.tibble(cbind(colMeans(formatted_rev_mix_fit_chiffre_id),t(apply(formatted_rev_mix_fit_chiffre_id, 2, FUN = quant))))

exp2_mix<-as.tibble(cbind(colMeans(formatted_rev_mix_fit_exp2_id),t(apply(formatted_rev_mix_fit_exp2_id, 2, FUN = quant))))

formatted_barre_mix <- barre_mix %>%
  select(mean = `V1`, low = `5%`, hi = `95%`) %>%
  mutate(mean = round(mean, 2)) %>%
  mutate(low = round(low, 2)) %>%
  mutate(hi = round(hi, 2)) %>%
  mutate(confint = paste0("[", low ,";",hi,"]")) %>%
  select(mean,confint)

formatted_chiffre_mix <- chiffre_mix %>%
  select(mean = `V1`, low = `5%`, hi = `95%`) %>%
  mutate(mean = round(mean, 2)) %>%
  mutate(low = round(low, 2)) %>%
  mutate(hi = round(hi, 2)) %>%
  mutate(confint = paste0("[", low ,";",hi,"]")) %>%
  select(mean,confint)

formatted_exp2_mix <- exp2_mix %>%
  select(mean = `V1`, low = `5%`, hi = `95%`) %>%
  mutate(mean = round(mean, 2)) %>%
  mutate(low = round(low, 2)) %>%
  mutate(hi = round(hi, 2)) %>%
  mutate(confint = paste0("[", low ,";",hi,"]")) %>%
  select(mean,confint)

Parameters<-c("$\\bar{N}$","$\\alpha$","$\\bar{I}$","$\\bar{m}$","$\\bar{\\lambda}$","$\\bar{\\gamma}$","$\\bar{\\beta}$","$\\bar{\\stay}$")
tab <- cbind(Parameters,formatted_barre_mix, formatted_chiffre_mix,formatted_exp2_mix)

colnames(tab) <- c("Parameters","Mean","$90\\%$ CI","Mean","$90\\%$ CI","Mean","$90\\%$ CI")


library(kableExtra)
x=kable(tab, format = "latex", caption = "Parameter estimates, by individual, mixed model", booktabs = TRUE, digits=2, escape=F) %>% save_kable("tables/tab_mixed_individual.tex")

library(latexpdf)
as.pdf(tab, stem="mix_individual")
file.rename(from="mix_individual.pdf",to="./tables/mix_individual.pdf")

```

## storing individual parameter estimates

```{r}
# doing distribution of parameter estimates, by treatment
# but need to put variables in correct order --> c(2,5,3,4,6,7,8) is I, gamma, m, lambda, beta, stay

a<-cbind(rep(1,length(formatted_rev_mix_fit_barre_id[,1])),formatted_rev_mix_fit_barre_id[,c(3,6,4,5,7,8,2)])
colnames(a)<-c("treatment","I","gamma","m","lam","beta","stay","alpha")


b<-cbind(rep(2,length(formatted_rev_mix_fit_chiffre_id[,1])),formatted_rev_mix_fit_chiffre_id[,c(3,6,4,5,7,8,2)])
colnames(b)<-c("treatment","I","gamma","m","lam","beta","stay","alpha")
c<-cbind(rep(3,length(formatted_rev_mix_fit_exp2_id[,1])),formatted_rev_mix_fit_exp2_id[,c(3,6,4,5,7,8,2)])
colnames(c)<-c("treatment","I","gamma","m","lam","beta","stay","alpha")

#individual_parameter_estimates<-a
individual_parameter_estimates<-rbind(a,b,c)


write.csv(individual_parameter_estimates,file="./results/individual_parameter_estimates.csv", row.names = FALSE)
```

## graphs of individual parameter estimates

```{r}


individual_parameter_estimates<-read.csv("./results/individual_parameter_estimates.csv")

a<-individual_parameter_estimates$treatment
a<-factor(a)
#levels(a) = c("Graph")
levels(a) = c("Graph", "Num", "Exp~2")
individual_parameter_estimates$treatment<-a

individual_parameter_estimates$lambda<-individual_parameter_estimates$lam

# distribution and correlation of parameters

p<-ggpairs(individual_parameter_estimates, 
        columns = c("I", "gamma", "m","lambda","beta","stay"), 
        ggplot2::aes(colour=factor(treatment), alpha=0.3),
        diag = list(continuous = "densityDiag", discrete = "barDiag", na = "naDiag"))+
    theme_minimal()

png(file=paste("./graphs/individual_parameters_correlations.png",sep=""),width=600, height=350)
p
dev.off()


### Alternative code to get better resolution and consistent plot
individual_parameter_estimates<-read.csv("./results/individual_parameter_estimates.csv") %>% as_tibble()


plotme <- individual_parameter_estimates %>% 
  select(treatment, I, gamma, m, lambda = lam, beta, stay) %>% 
  mutate(treatment = case_when(treatment == 1 ~ "Graphical",
                               treatment == 2 ~ "Numeric", 
                               treatment == 3 ~ "Exp2")) %>% 
  mutate(treatment = as.factor(treatment),
         treatment = fct_relevel(treatment, "Graphical", "Numeric"))



#install.packages("hrbrthemes", repos = c("https://cinc.rud.is", "https://cloud.r-project.org/"))
## attraction
plotme %>% 
  ggpairs( 
        columns = c("I","gamma","m", "lambda", "beta","stay"), 
        ggplot2::aes(colour=factor(treatment), alpha=0.3),
        labeller = "label_parsed",
        diag = list(continuous = "densityDiag", discrete = "barDiag", na = "naDiag"))+
  hrbrthemes::theme_ipsum()
ggsave("./graphs/individual_parameter_correlation_better.png", width = 16/1.5, height = 12/1.5, 
       units = "in", dpi = 300)



```

## tables of speed, precision, bias, etc using example options and mean of individual estimates

```{r}
# spell out simulated options, a is for attraction effect, s is for similarity, c is for compromise

# attraction
scaling<-4

options_a<-rbind(c(6, 4, 4, 6, 6, 3.4),c(4, 6, 6, 4, 3.4, 6))/scaling

#similarity

options_s<-rbind(c(6, 4, 4, 6, 3.8, 6.2), c(4, 6, 6, 4, 6.2, 3.8))/scaling


#compromise

options_c<-rbind(c(6, 4, 4, 6, 8, 2), c(4, 6, 6, 4, 2, 8))/scaling
```


## compute summary indicators for each effect

```{r}
individual_parameter_estimates<-read.csv("./results/individual_parameter_estimates.csv")


fit_formatted<-individual_parameter_estimates


for (i in 1:3){

  if (i==1) {
  effect<-"attraction"
  options<-options_a
  J<-length(options[,1]) #(nr of menus)
} else if (i==2) {
    effect<-"similarity"
    options<-options_s
    J<-length(options[,1]) #(nr of menus)
} else {
      effect<-"compromise"
      options<-options_c
      J<-length(options[,1]) #(nr of menus)
}





# computing the drifts and other indicators (here, adapt with alpha parameter)

rep<-1 # number of repetitions, only one as deterministic here
N<-length(fit_formatted$treatment) # number of people
rt_test<-matrix(data=NA,nrow=J*N*rep,ncol=21) # to store estimates
for(l in (1:rep)){
for (j in (1:J)){
for (i in (1:N)){
  rt_test[((l-1)*N*J+(i+N*(j-1))),1:4]<-c(i,j,l,((l-1)*N*J+(i+N*(j-1))));
  rt_test[((l-1)*N*J+(i+N*(j-1))),5:10]<-options[j,];
  rt_test[((l-1)*N*J+(i+N*(j-1))),11:13]<-getDrifts(options[j,],fit_formatted$I[i],fit_formatted$m[i],fit_formatted$lam[i],fit_formatted$gamma[i],fit_formatted$beta[i]); #drifts first choice  

  rt_test[((l-1)*N*J+(i+N*(j-1))),14]<-(fit_formatted$I[i]+0.15*fit_formatted$gamma[i])/gamma(1+1/fit_formatted$alpha[i]); #this is speed if there was a value difference of 0.6/4 between options, as between T and D
  rt_test[((l-1)*N*J+(i+N*(j-1))),15]<-((fit_formatted$I[i]+0.15*fit_formatted$gamma[i])/max(fit_formatted$I[i]-0.15*fit_formatted$gamma[i],0.00000000001))^fit_formatted$alpha[i]/(1+((fit_formatted$I[i]+0.15*fit_formatted$gamma[i])/max(fit_formatted$I[i]-0.15*fit_formatted$gamma[i],0.00000000001))^fit_formatted$alpha[i]); #this is precision if there was a value difference of 0.6/4. Note need to set =1 if second is negative
  rt_test[((l-1)*N*J+(i+N*(j-1))),16]<-fit_formatted$treatment[i];
  rt_test[((l-1)*N*J+(i+N*(j-1))),17:19]<-(rt_test[((l-1)*N*J+(i+N*(j-1))),11:13]-fit_formatted$I[i])/fit_formatted$gamma[i]; # this is the value differences   


  
    rt_test[((l-1)*N*J+(i+N*(j-1))),20]<-fit_formatted$stay[i]; # this is the stay parameter
    rt_test[((l-1)*N*J+(i+N*(j-1))),21]<-fit_formatted$alpha[i]; # this is the alpha parameter
}
}
}

if (effect=="attraction") {
  rt_test_a<-rt_test
} else if (effect=="similarity") {
    rt_test_s<-rt_test
} else {
      rt_test_c<-rt_test
}

}
```


## once all rt_test for all effects are computed:

```{r}
# then store bias and shares depending on what was computed

shares_attraction<-rt_test_a[,11:13]^rt_test_a[,21]/rowSums(rt_test_a[,11:13]^rt_test_a[,21])
shares_similarity<-rt_test_s[,11:13]^rt_test_s[,21]/rowSums(rt_test_s[,11:13]^rt_test_s[,21])
shares_compromise<-rt_test_c[,11:13]^rt_test_c[,21]/rowSums(rt_test_c[,11:13]^rt_test_c[,21])
#View(shares)

#bias<-rowSds(shares)


bias_attraction<-rowSds(rt_test_a[,17:19])
bias_similarity<-rowSds(rt_test_s[,17:19])
bias_compromise<-rowSds(rt_test_c[,17:19])


# once done, store in matrix
rt_test<-rt_test_a
#rt_test<-cbind(rt_test,bias_attraction)

rt_test<-cbind(rt_test,bias_attraction,bias_similarity,bias_compromise,shares_attraction,shares_similarity,shares_compromise)
colnames(rt_test)
#colnames(rt_test)<-c("id","menus","rep","rep2","t1","t2","c1","c2","d1","d2","drift1","drift2","drift3","speed","precision","treatment","f1","f2","f3","stay","alpha","bias_att")
colnames(rt_test)<-c("id","menus","rep","rep2","t1","t2","c1","c2","d1","d2","drift1","drift2","drift3","speed","precision","treatment","f1","f2","f3","stay","alpha","bias_att","bias_sim","bias_comp","target_a","comp_a","dec_a","target_s","comp_s","dec_s","target_c","comp_c","dec_c")

summary(rt_test)

write.csv(rt_test,file="./results/individual_indicators.csv", row.names = FALSE)


library(tibble)
rt_test<-as.tibble(rt_test)

# summary by experiment (graphical,numeric, exp2)

summary(rt_test[rt_test$treatment==1,]) 
summary(rt_test[rt_test$treatment==2,]) 
summary(rt_test[rt_test$treatment==3,]) 
 


# then need to do average by variable id

rt_test_mean<-data.frame(matrix(NA,ncol=1,nrow=length(rt_test$id)/2))
rt_test_mean$treatment<-tapply(rt_test$treatment, rt_test$id, mean)

rt_test_mean$speed<-tapply(rt_test$speed, rt_test$id, mean)
rt_test_mean$precision<-tapply(rt_test$precision, rt_test$id, mean)
rt_test_mean$target_a<-tapply(rt_test$target_a, rt_test$id, mean)
rt_test_mean$comp_a<-tapply(rt_test$comp_a, rt_test$id, mean)
rt_test_mean$dec_a<-tapply(rt_test$dec_a, rt_test$id, mean)
rt_test_mean$bias_a<-tapply(rt_test$bias_att, rt_test$id, mean)

rt_test_mean$target_s<-tapply(rt_test$target_s, rt_test$id, mean)
rt_test_mean$comp_s<-tapply(rt_test$comp_s, rt_test$id, mean)
rt_test_mean$dec_s<-tapply(rt_test$dec_s, rt_test$id, mean)
rt_test_mean$bias_s<-tapply(rt_test$bias_sim, rt_test$id, mean)

rt_test_mean$target_c<-tapply(rt_test$target_c, rt_test$id, mean)
rt_test_mean$comp_c<-tapply(rt_test$comp_c, rt_test$id, mean)
rt_test_mean$dec_c<-tapply(rt_test$dec_c, rt_test$id, mean)
rt_test_mean$bias_c<-tapply(rt_test$bias_comp, rt_test$id, mean)

rt_test_mean$stay<-tapply(rt_test$stay, rt_test$id, mean)

write.csv(rt_test_mean,file="./results/individual_indicator_estimates.csv", row.names = FALSE)



# graphing results, first method

p_attraction<-ggpairs(rt_test_mean[,], 
        columns = c("speed","precision","bias_a","bias_s","bias_c","stay"), 
        ggplot2::aes(colour=factor(treatment), alpha=0.3),
        diag = list(continuous = "densityDiag", discrete = "barDiag", na = "naDiag"))+
    theme_minimal()

png(file=paste("./graphs/individual_indicator_correlations_attraction.png",sep=""),width=600, height=350)
p_attraction
dev.off()


# graphing results, second method
plotme <- rt_test_mean %>% 
  select(treatment, Speed = speed, Precision = precision, bias_a, bias_s, bias_c, Stay = stay) %>% 
  mutate(treatment = case_when(treatment == 1 ~ "Graphical",
                               treatment == 2 ~ "Numeric", 
                               treatment == 3 ~ "Exp2")) %>% 
  mutate(treatment = as.factor(treatment),
         treatment = fct_relevel(treatment, "Graphical", "Numeric"))

## attraction
plotme %>% 
  select(treatment, Speed, Precision, Bias = bias_a, Stay) %>% 
  ggpairs( 
        columns = c("Speed","Precision","Bias","Stay"), 
        ggplot2::aes(colour=factor(treatment), alpha=0.3),
        diag = list(continuous = "densityDiag", discrete = "barDiag", na = "naDiag"))+
  hrbrthemes::theme_ipsum()
ggsave("./graphs/individual_indicator_correlation_attraction_better.png", width = 16/1.5, height = 12/1.5, 
       units = "in", dpi = 300)

## similarity
plotme %>% 
  select(treatment, Speed, Precision, Bias = bias_s, Stay) %>% 
  ggpairs( 
        columns = c("Speed","Precision","Bias","Stay"), 
        ggplot2::aes(colour=factor(treatment), alpha=0.3),
        diag = list(continuous = "densityDiag", discrete = "barDiag", na = "naDiag"))+
  hrbrthemes::theme_ipsum()
ggsave("./graphs/individual_indicator_correlation_similarity_better.png", width = 16/1.5, height = 12/1.5, 
       units = "in", dpi = 300)

## compromise
plotme %>% 
  select(treatment, Speed, Precision, Bias = bias_c, Stay) %>% 
  ggpairs( 
        columns = c("Speed","Precision","Bias","Stay"), 
        ggplot2::aes(colour=factor(treatment), alpha=0.3),
        diag = list(continuous = "densityDiag", discrete = "barDiag", na = "naDiag"))+
  hrbrthemes::theme_ipsum()
ggsave("./graphs/individual_indicator_correlation_compromise_better.png", width = 16/1.5, height = 12/1.5, 
       units = "in", dpi = 300)
```

## table of summary individual indicator estimates

```{r}

rt_test_mean <- read_csv("./results/individual_indicator_estimates.csv")

rt_test_mean<-rt_test_mean[,-1]

rt_test_mean<-as.data.frame(rt_test_mean)
#library(doBy)
# 
# indicators_att<-summaryBy(speed + precision + bias_att + stay ~ treatment, data = rt_test_mean,
#   FUN = function(x) { c(m = mean(x), q5 = quantile(x, probs = 0.05), q95 = quantile(x, probs = 0.95)) } )

ff_d <- melt(rt_test_mean, id.vars="treatment", na.rm=TRUE)
cast_ff_d<-cast(ff_d, variable ~ treatment, function(x) c(mean(x), quantile(x,c(0.05,0.95))))

formatted_indicators_1 <- cast_ff_d %>%
  select(variable= variable, mean = `1_X`, low = `1_X5.`, hi = `1_X95.`) %>%
  mutate(mean = round(mean, 2)) %>%
  mutate(low = round(low, 2)) %>%
  mutate(hi = round(hi, 2)) %>%
  mutate(confint = paste0("[", low ,";",hi,"]")) %>%
  select(variable, mean,confint)

formatted_indicators_2 <- cast_ff_d %>%
  select(variable= variable, mean = `2_X`, low = `2_X5.`, hi = `2_X95.`) %>%
  mutate(mean = round(mean, 2)) %>%
  mutate(low = round(low, 2)) %>%
  mutate(hi = round(hi, 2)) %>%
  mutate(confint = paste0("[", low ,";",hi,"]")) %>%
  select(mean,confint)

formatted_indicators_3 <- cast_ff_d %>%
  select(variable= variable, mean = `3_X`, low = `3_X5.`, hi = `3_X95.`) %>%
  mutate(mean = round(mean, 2)) %>%
  mutate(low = round(low, 2)) %>%
  mutate(hi = round(hi, 2)) %>%
  mutate(confint = paste0("[", low ,";",hi,"]")) %>%
  select(mean,confint)

Parameters<-c("Mean","$90\\%$ CI","Mean","$90\\%$ CI","Mean","$90\\%$ CI")
tab <- cbind(formatted_indicators_1, formatted_indicators_2, formatted_indicators_3)

library(kableExtra)
x=kable(tab, format = "latex", caption = "Indicator estimates, by individual, mixed model", booktabs = TRUE, digits=2, escape=F) %>% save_kable("tables/tab_mixed_individual_indicators.tex")

library(latexpdf)
as.pdf(tab, stem="mix_individual_indicators")
file.rename(from="mix_individual_indicators.pdf",to="./tables/mix_individual_indicators.pdf")



write.csv(tab,file="./results/individual_indicator_estimates_stats.csv", row.names = FALSE)



```

